Geometrization of characters of tori over non-Archimedean local fields

### 2013-07-31 shanghai.tex
Added on our result about the tranfer principle

\section{Functorial properties of the main isomorphism}

@@

We recall the notion of $N$-congruent tori from \cite[\S 2]{CY}.  Suppose $T$ and $T'$
are tori over non-Archimedian local fields $K$ and $K'$, splitting over $L$ and $L'$ respectively.

@@

>>>>

@@

\David{We should add a discussion of why we care about the transfer principle.}
We recall the notion of $N$-congruent tori from \cite[\S 2]{CY}.  Suppose $T$ and $T'$
are tori over non-Archimedian local fields $K$ and $K'$, splitting over $L$ and $L'$ respectively.

@@

As an immediate consequence of this theorem and Theorem \ref{thm:application} we have the following corollary:

\begin{corollary}
 Suppose that $T$ and $T'$ are $N$-congruent for $N > 3h$.  Then there is a canonical equivalence of categories
 \[
  \CS(\GN{T}_{N-3h}) \to \CS(\GN{T}'_{N-3h})
 \]
 determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
 \[
  \Hom(T(K) / T(K)_{N-3h}, \EEx) \to \Hom(T'(K') / T'(K')_{N-3h}, \EEx)
 \]
\end{corollary}
